Local Group Satellite Alignments

### 2017-07-26 paper/paper.tex
new plot in paper
cum ditro beta
new plots into the paper
remove cosmic web

We compute the cosmic web from the DM information in the
Illustris-3 simulation which share the same structure information with
Illustris-1 on scales of $1$ Mpc.  
Illustris-3 has $456^3$ DM particles, corresponding to
$4.0\times 10^8$ \Msun in DM particle mass and $5.7$ kpc for the DM
gravitational softwning lentgh.

@@

\section{Cosmic Web Calculations}
\label{sec:CosmicWeb}

We place the LGA pairs into the cosmic web as quantified by the
deformation tensor  
\citep{2007MNRAS.375..489H,2009MNRAS.396.1815F}.
This method computes a cartesian grid the tidal tensor 
\begin{equation}
T_{ij} \equiv \frac{\partial^2\phi}{\partial r_i \partial r_j},
\end{equation}
%
where $\phi$ is a pseudo-gravitational potential that satisfies the
Poisson equation $\nabla^2\phi=\delta$, with $\delta$ the DM matter
overdentisy, and the $r_i$ coordinates correspond to a cartesian
system with $i=1,2,3$.

This tensor can be diagonalized.
Its eigenvalues ($\lambda_1 > \lambda_2 > \lambda_3$) and
corresponding eigenvectors ($\hat{e}_1$, $\hat{e}_2$, $\hat{e}_3$)
define the degree and direction of stability around the neighborhood
where the tensor is computed. 
This allows the classification of that region either as a peak,
filament, sheet or voids in the case of three, two, one or zero
eigenvalues larger than a given threshold $\lambda_{\rm th}$.

In this study we compute these eigenvalues and eigenvectors over the
dark matter component of the Illustris-3 simulation on a cubic mesh of
$74$ cells on a side. 
This resolution corresponds to $\sim 1$ \Mpch.
We interpolate the DM density on that mesh using a Cloud-In-Cell (CIC)
scheme, then smooth the density field with a gaussian window with a
physical scale equal to the cell size.

We choose this interpolation and smoothing scale for two reasons.
First, because it corresponds to the typical pair separation in our
sample, making each halo in the pair share the same environment.
Second, because it allows a direct comparison with previous results in
the literature that used the same setup to quantify the cosmic
web environment for Local Group pairs in a cosmological context
\citep{ForeroRomero2013,2015ApJ...799...45F}.

@@

\begin{enumerate}
\item{The inertia tensor}.
\item{Fitting planes}.
\item{Velocity Anisotropy}.
\item{Alignment with the cosmic web}. 
\end{enumerate}

@@

\begin{table*}
  \centering
\begin{tabular}{lll}
\hline\hline
Symbol & Units & Description\\\hline
$M_{\star}$ & $10^{10}$\Msun & Stellar mass of the central galaxy\\
$N_s$ & & Number of satellites with $M_V<-9$\\
$a > b> c$ & & Inertia tensor eigenvalues. \\
$\hat{I}_a$, $\hat{I}_b$, $\hat{I}_c$ & & Inertia tensor eigenvectors. \\
$\beta$  &  & Satellite Velocity Anisotropy\\
$\sigma_s$ & kpc & Plane width\\
$\lambda_1>\lambda_2>\lambda_3$ &  & Tidal tensor
eigenvalues\\
$\hat{e}_{1}$,  $\hat{e}_{2}$,  $\hat{e}_{3}$ &  & Tidal tensor
eigenvectors\\ 
$\hat{r}_{AB}$& & Unit vector in the direction to the galaxy companion\\
\hline\hline
\end{tabular}
  \caption{Overview of the parameters computed for each central galaxy
    and its satellite system.
  \label{tab:models}}
\end{table*}

\subsection{Cosmic Web Alignment}
\label{sub:webalignment}

\cite{2015ApJ...799...45F} showed tha LGA pairs present alignments
with the cosmic web.
The strongest alignment is between the eigenvector associated  with the smallest
eigenvalue, $\hat{e}_3$, and the vector $\hat{r}_{AB} $connecting the two halos in
the pair. 
The eigenvector $\hat{e}_3$ indicates the direction along
which the cosmic web filament lies and in the case of being on a local
sheet it is a vector lying on the pancakes' plane.

Following \cite{2014MNRAS.443.1090F} we compute the closest cosmic web
eigenvalue  towards which the vectors $\hat{r}_{AB}$, $\hat{p}$ and
$\hat{I}_a$ are aligned.

>>>>

@@

@@

\begin{enumerate}
\item{The inertia tensor}.
\item{Fitting planes}.
\item{Velocity Anisotropy}.
\end{enumerate}

@@

\begin{table*}
  \centering
\begin{tabular}{lll}
\hline\hline
Symbol & Units & Description\\\hline
$M_{\star}$ & $10^{10}$\Msun & Stellar mass of the central galaxy\\
$N_s$ & & Number of satellites with $M_V<-9$\\
$a > b> c$ & & Inertia tensor eigenvalues. \\
$\hat{I}_a$, $\hat{I}_b$, $\hat{I}_c$ & & Inertia tensor eigenvectors. \\
$\beta$  &  & Satellite Velocity Anisotropy\\
$\sigma_s$ & kpc & Plane width\\
$\hat{r}_{AB}$& & Unit vector in the direction to the galaxy companion\\
\hline\hline
\end{tabular}
  \caption{Overview of the parameters computed for each central galaxy
    and its satellite system.
  \label{tab:models}}
\end{table*}

\section{Results}
\label{sec:results}

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{planes.pdf}
\caption{
Plane width as a function of the number of bright satellites.
Wider planes are expected as the satellite number increases.
\label{fig:planes}}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{beta.pdf}
\caption{
Cumulative distribution for the gelocity anisotropy $\beta$.
\label{fig:beta}}
\end{figure}

\begin{figure*}
\centering
\includegraphics[width=0.48\textwidth]{mu_ri_cum.pdf}
\includegraphics[width=0.48\textwidth]{mu_ri_scatter.pdf}
\caption{
Cumulative distribution for the gelocity anisotropy $\beta$.
\label{fig:mu_ri}}
\end{figure*}
